Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
spalling mystaces
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\begin{abstract}
Storage systems are caught between rapidly changing data processing systems and
the increasing speed of storage devices. This puts tremendous pressure on
storage systems to adapt both in terms of their interfaces and their
performance. But adapting storage systems can be difficult because unprincipled
changes might jeopardize years of code-hardening and performance optimization
efforts that were necessary for users to entrust their data to the storage
system.  We introduce  Malacology, a prototype programmable storage system to
explore how existing abstractions of common services found in storage systems
can be leveraged to address new data processing systems and the increasing
speed of storage devices. This approach allows unprecedented flexibility for
storage systems to evolve without sacrificing the robustness of its
code-hardened subsystems.  We illustrate the advantages and challenges of
programmability by constructing two services out of existing abstractions: a
file system metadata load balancer and a high-performance distributed shared-log
that leverages flash devices.  RESULTS
\end{abstract}

@@

A number of recent developments are disrupting traditional storage
systems: (1) the falling prices of flash storage and the availability of
new types of non-volatile memory that are orders of magnitude faster
than traditional spinning media are moving overall performance
bottlenecks away from storage devices to CPUs and networking, and
pressure storage systems to shorten their code paths and incorporate new
optimizations~\cite{gray_tape_2007,gray_flash_2008}; (2) demand for managing structured data and flexible
consistency semantics at scale pressure big data processing systems to
use storage abstractions that can meet these demands~\cite{apache_contributors_parquet_2014}; and (3)
production-quality scalable storage systems available as open source
software have established and are continuing to establish new, \emph{de
facto} API standards at a faster pace than traditional standards bodies~\cite{snia_implementing_2014,linux_foundation_kinetic_2015}.

\begin{figure}[tb]
\centering
\includegraphics{figures/overview.png}
\caption{A Ceph installation consists of a cluster running mostly
storage daemons (OSDs) to ensure data durability, a few monitor daemons
(MONs) to reach consensus of the cluster state and to ensure its
consistent versioning, and a few metadata service daemons (MDSs) for
scalable metadata service. Ceph's APIs include object, block, file
abstractions. Malacology enables the programmability of these
abstractions and services (indicated by bold arrows). To illustrate Malacology we implement two
services on Ceph, Zlog and Mantle, by programming Ceph's durability,
consistent versioning, consensus, and metadata subsystems.
\label{fig:overview}}
\end{figure}

@@

In this paper we investigate an approach that focusses on generalizing
existing storage system resources, services, and abstractions that in
generalized form can be used to \emph{program} new services. By doing so
one can reuse subsystems and leverage their optimizations,
established correctness, robustness, and efficiency. We will refer to
this programmability as \emph{programmable storage}, which differs from
\emph{active storage} (the injection and execution of arbitrary code in
a storage system) and \emph{software-defined storage} (the control of
thin-provisioning of storage).

@@

To illustrate the benefits and challenges of this approach we have
designed and evaluated Malacology, a programmable storage system for
constructing new services by re-purposing existing subsystem
abstractions contained in Ceph. We build the framework in Ceph by
leveraging a broad spectrum of existing services, including distributed
locking and caching services provided by MDSs, durability and logical
storage devices provided by RADOS, and propogation of consistent cluster
state provided by the monitoring service (see Figure~\ref{fig:overview}). As we will show in this paper, this framework is expressive enough to provide the
functionality necessary for implementing new services. Our contributions
are:

@@

  \begin{enumerate}
%  \def\labelenumi{\arabic{enumi}.}
%  \itemsep1pt\parskip0pt\parsep0pt
  \item
    A high-performance distributed shared log service called Zlog which is based on CORFU~\cite{balakrishnan_corfu_2012}
  \item
    A re-implementation of the programmable Mantle metadata load balancing service~\cite{sevilla:sc15-mantle} using Malacology
  \item 
    An application of Mantle to manage load-balancing of sequencers.
  \end{enumerate}

@@

There are multiple reasons that make Lua an attractive runtime for implementing 
Malacology. Lua is a portable, embedded
scripting language that offers superious performance and productivity
trade-offs, including a JIT-based implementation that is well known for near
native performance. Additionally, Lua has been used extensively in game engines, 
and systems research \cite{neto:dls14-luaos}, including storage systems where it 
has been effectively used both on
\cite{grawinkel:pdsw2012-lua,watkins2013:bdmc13-in-vivo,geambasu_comet_2010} and 
off
\cite{sevilla:sc15-mantle} the performance critical path. Finally, the 
flexibility of the runtime allows to sandbox applications in order to address 
security and performance concerns.

@@

Briefly described in Section~\ref{sec:intro}, Ceph supports the creation
of application-specific object interfaces~\cite{weil_rados_2007}. The ability
to offload computation can reduce data movement, and transactional interfaces can
significantly simplify construction of complex storage interfaces that require
uncoordinated parallel access.

An object interface is a plugin structured in a similar way to that of an RPC
in which a developer creates a named function within the cluster that clients
may invoke. In the case of Ceph each function is implicitly run within the
context of an object specified when the function is invoked. Developers of
object interfaces express behavior by creating a composition of native
interfaces or other custom object interfaces, and handle serialization of
function input and output. A wide range of native interfaces are available to
developers, such as reading and writing to a bytestream, controlling snapshots
and clones, all of which may be transactionally composed with access to a
sorted key-value service allowing applications to create rich interfaces, such
as using a read-modify-write guard to protect a shared index defined over
content store in a byte stream.

\begin{figure}[htbp]
\centering
\includegraphics{figures/implementation.png}
\caption{Malacology re-uses Ceph subsystems to manage interface classes.
command. After the proposal is accepted by the cluster of monitors, the
script is redundantly and consistently distributed to OSDs.
\label{fig:implementation}}
\end{figure}

@@

To this end we have extended the monitoring service using the framework
described in Section~\ref{sec:mon} to provide an interface for registration
and verification of dynamically defined object interfaces. Using this service
guarantees that interface definitions are not only made durable, but are
transparently and consistently propogated throughput the cluster and that
clients are properly synchronousized with the latest interfaces.

@@

\paragraph*{Malacology:} New interface hooks are added in strategic spots in
the metadata service to control load balancing and capabilities, and for
defining new file types allowing the indexing service to be repurposed for
other types of named resources.

@@

{\bf Safely Loading Classes.} The original Mantle API is fragile: the API is
not enforced by the runtime, the system allows injectable strings through the
admin daemon, constructing the Lua script in C++ is clunky, and the
administrator can inject really bad policies (e.g., while 1) that brings the
whole system down. Malacology exposes the important subsystems of Ceph's
logical storage device framework so that the MDS can safely and dynamically
load policies specified as Lua classes.

@@

The clients retain the best-effort, voluntary release of capabilities, but in
Malacology, the queuing policies are generalized within the MDS to allow for
centeralized policies such as fairness or priority.

@@

Ceph provides storage by striping and replicating data across
RADOS~\cite{weil_rados_2007}, the reliable distributed object store. RADOS
uses many techniques to ensure that data is not corrupted or lost, such as
erasure coding, replication, and data scrubbing. Furthermore, many of these
techniques try to be autonomous so that work is distributed across the
cluster. For example, when placement groups change, the OSDs rebalance and
re-shard data in the background in a process called placement group splitting.

@@

\paragraph*{Malacology:} Metadata service policies and object storage interfaces are stored durability
within RADOS and managed by storing references with the object maps. Since
the cluster already propagates a consistent view of these data structures,
we use this service to automatically install interfaces in OSDs, and install
policies within the MDS such that clients and daemons are synchronzied on
correct implementations without restarting.

@@

High-performance in CORFU is achived using a sequencer service that assigns
log positions to clients by reading from a volatile, in-memory counter which
can run at a very high throughput and at low-latency. And since the sequencer
is centralized, ensuring seiralizability in the common case is trivial.  The
primary challenge in CORFU is handling the failure of the sequencer in a way
that preserves correctness. Failure of the sequencer service in CORFU is
handled by a recovery algorithm that recomputes the new sequencer state using
an application-specific custom storage interface to discover the tail of the
log, while simulatenously invalidating stale client requests using an
epoch-based protocol.

@@

Initially we sought to directly model the sequencer service in Ceph as a
non-exclusive, non-cacheable resource, forcing clients to perform a round-trip
access to the resource at the authoratiave metadata server for the sequencer
inode.  Interestingly, we found that the capapbility system in Ceph uses a
strategy to reduce metadata service load by allowing multiple clients that
open a shared file to temporarily cache the inode resource, resulting in a
round-robin, best-effort batching behavior. When a single client is accessing
the sequencer resource it is able to cache state locally without interruption.

@@

The storage interface is a critical component in the CORFU design. Clients
independently map log positions that they have obtained from a sequencer
service (described in detail in the next seciton) onto storage devices, while
storage devices provide an intelligent \emph{write}-once, random \emph{read}
interface for accessing log entries. The key to correctness in CORFU lies with
the enforcement of up-to-date epoch tags on client requests; requests tagged
with out-of-date epoch values are rejected, and clients are expected to
request a new tail from the sequencer after refreshing state from an auxillary
service.  This mechanism forms the basis for sequencer recovery.

In order to repopulate the cached tail value during recovery of a sequencer,
the maximum position in the log must be obtained. To do this, the storage
interface exposes an additional \emph{seal} method that atomically installs a
new epoch value and returns the maximum log position that has been written.
Since the recovery protocol does not inform clients of a new epoch value until
the end of the process, the validity of the tail can be guaranteed despite the
iterative process of contacting storage devices.  Recovery of the sequencer
process itself may be handled in many ways, such as leader election using an
auxillary service such as PAXOS.

@@

We evaluate the mapping of ZLog onto Malacology by examining the costs of
utilizing the metadata service as a sequencer, and propogating interface
changes throughout the cluster using the monitoring service. We have omitted
evaluation of the overhead costs of adding object interfaces themselves due to
lack of space, and the fact that they are heavily tested and used already in
production with acceptable performance, introducing a small constant overhead
per operation but otherwise does not affect scalability.

@@

\begin{figure}[h]
\centering
\includegraphics{figures/caps-delay-thruput.png}
\caption{Sequencer throughput by reusing various services.
The highest performance is achieved using a single client with
exclusive, cacheable priviledge. Round-robin sharing of the sequencer
resource is affected by the amount of time the resource is held,
with best-effort performing the worst.}
\label{fig:captp}
\end{figure}

@@

While a best-effort approach to sharing capabilities makes sense for a file
system client, throughput drops significantly with two clients as the majority
of the time neither client has the capapbitility as it ping-pongs between
clients. This observation reveals a tuning parameter: how long a client
maintains its capapbility lease. In throughputs labeled $2C,<time>$ we show
aggregate throughput as we decrease the amount of time that a client holds its
lease before responding to a request for the capapbility.  At lease times as
low as 10ms throughputs achieve a significant proportion of the locally cached
throughput.

\textbf{The Malacology Approach:} Re-use the capability management features of the MDS.
While the batching mechanism can achieve high-throughput, it is not appropriate
for applications that require predictable latency. The throughput in
Figure~\ref{fig:captp} labeled $2C,ZLog$ corresponds to a centeralized
sequencer implementation. While throughput is lower for two clients (because of
the synchronous network round-trip required for each request),
Figure~\ref{fig:capcdf} shows that this approach achieves more predicable
latency compared to all other approaches except for the single client locally
cached mode.

\subsubsection{Interface Propogation}

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-seq-thruput.png}
\caption{A ZLog sequencer that uses the CephFS MDS enjoys the load balancing
capabilities of the metadata cluster. The ``Sequencer Baseline'' has no
background sequencers, while the the ``2 Seq'' curves are the throughputs
of 1 sequencer when an additional sequencer is running in the background
generating load.}\label{fig:mantle-seq-thruput}
\end{figure}

@@

Figure~\ref{fig:mantle-cpu-utilization} gives a time series graph to show the
behavior of the same workload, 2 sequencers, with balancing turned on and off.
The curves are the throughputs (\(y\) axis) over time (\(x\) axis) and the graph
has been partitioned into the two cluster setups. The CPU utilization is
confined to one core the MDS is not multithreaded, as it has been shown that
metadata performance does not improve with multiple
threads~\cite{konstantinos:pdsw2014-lustre-metadata}.

Overall, the clients achieve lower performance than the capability experiments
in Figure~\ref{fig:captp} because the sequencer uses a slower metadata
operation to manage the capability.  ``Sequencer Baseline" is the best
performance for this particular workload because there is no contention.
Performance is stable and the MDS is underloaded because we do not see the
spike at the end like the other curves. It appears the bottleneck is somewhere
with the clients -- perhaps it is our 1GBit/s network link. ``2 Seq; No Load
Balancing" shows an overloaded sequencer because the performance of our one
sequencer is low and unstable (high variation in performance). We also deduce
that it is overloaded by comparing to the ``2 Seq; Mantle Load Balancing"
curve, which shows improved performance when load is migrated. At 10 seconds,
the sequencer balancer immediately starts balancing and decides that two
sequencer streams should be split onto two MDSs. It migrates to its neighbor as
per the policy.

@@

We are intend to pursue this work towards the goal of constructing a set
of customization points that allow a wide variety of storage system
services to be configured on-the-fly in existing systems. This work is
one point along that path in which we have looked an a target
special-purpose storage system. Ultimately we want to utilize
declarative methods for expressing new services.

In conclusion, this paper should be accepted.

>>>>

\begin{abstract}
Storage systems are caught between rapidly changing data processing systems and
the increasing speed of storage devices. This puts tremendous pressure on
storage systems to adapt both in terms of their interfaces and their
performance. But adapting storage systems can be difficult because unprincipled
changes might jeopardize years of code-hardening and performance optimization
efforts that were necessary for users to entrust their data to the storage
system.  We introduce  Malacology, a prototype programmable storage system to
explore how existing abstractions of common services found in storage systems
can be leveraged to address new data processing systems and the increasing
speed of storage devices. This approach allows unprecedented flexibility for
storage systems to evolve without sacrificing the robustness of its
code-hardened subsystems.  We illustrate the advantages and challenges of
programmability by constructing two services out of existing abstractions: a
file system metadata load balancer and a high-performance distributed shared-log
that leverages flash devices.
\end{abstract}

@@

A number of recent developments are disrupting traditional storage
systems: (1) the falling prices of flash storage and the availability of
new types of non-volatile memory that are orders of magnitude faster
than traditional spinning media are moving overall performance
bottlenecks away from storage devices to CPUs and networking, and
pressure storage systems to shorten their code paths and incorporate new
optimizations~\cite{gray_tape_2007,gray_flash_2008}; (2) demand for managing structured data and flexible
consistency semantics at scale pressure big data processing systems to
use storage abstractions that can meet these demands~\cite{apache_contributors_parquet_2014}; and (3)
production-quality scalable storage systems available as open source
software have established and are continuing to establish new, \emph{de-facto} API standards at a faster pace than traditional standards bodies~\cite{snia_implementing_2014,linux_foundation_kinetic_2015}.

\begin{figure}[tb]
\centering
\includegraphics{figures/overview.png}
\caption{A Ceph installation consists of a cluster running mostly
storage daemons (OSDs) to ensure data durability, a few monitor daemons
(MONs) to reach consensus of the cluster state and to ensure its
consistent versioning, and a few metadata service daemons (MDSs) for
scalable metadata service. Ceph's APIs include object, block, file
abstractions. Malacology enables the programmability of these
abstractions and services (indicated by bold arrows). To illustrate Malacology we implement two
services on Ceph, ZLog and Mantle, by programming Ceph's durability,
consistent versioning, consensus, and metadata subsystems.
\label{fig:overview}}
\end{figure}

@@

In this paper we investigate an approach that focuses on generalizing
existing storage system resources, services, and abstractions that in
generalized form can be used to \emph{program} new services. By doing so
one can reuse subsystems and leverage their optimizations,
established correctness, robustness, and efficiency. We will refer to
this programmability as \emph{programmable storage}, which differs from
\emph{active storage} (the injection and execution of arbitrary code in
a storage system) and \emph{software-defined storage} (the control of
thin-provisioning of storage).

@@

To illustrate the benefits and challenges of this approach we have
designed and evaluated Malacology, a programmable storage system for
constructing new services by re-purposing existing subsystem
abstractions contained in Ceph. We build the framework in Ceph by
leveraging a broad spectrum of existing services, including distributed
locking and caching services provided by MDSs, durability and logical
storage devices provided by RADOS, and propagation of consistent cluster
state provided by the monitoring service (see Figure~\ref{fig:overview}). As we will show in this paper, this framework is expressive enough to provide the
functionality necessary for implementing new services. Our contributions
are:

@@

  \begin{enumerate}
%  \def\labelenumi{\arabic{enumi}.}
%  \itemsep1pt\parskip0pt\parsep0pt
  \item
    A high-performance distributed shared log service called ZLog which is based on CORFU~\cite{balakrishnan_corfu_2012}
  \item
    A re-implementation of the programmable Mantle metadata load balancing service~\cite{sevilla:sc15-mantle} using Malacology
  \item 
    An application of Mantle to manage load-balancing of sequencers.
  \end{enumerate}

@@

There are multiple reasons that make Lua an attractive runtime for implementing 
Malacology. Lua is a portable, embedded
scripting language that offers superior performance and productivity
trade-offs, including a JIT-based implementation that is well known for near
native performance. Additionally, Lua has been used extensively in game engines, 
and systems research \cite{neto:dls14-luaos}, including storage systems where it 
has been effectively used both on
\cite{grawinkel:pdsw2012-lua,watkins2013:bdmc13-in-vivo,geambasu_comet_2010} and 
off
\cite{sevilla:sc15-mantle} the performance critical path. Finally, the 
flexibility of the runtime allows to sandbox applications in order to address 
security and performance concerns.

@@

Briefly described in Section~\ref{sec:intro}, Ceph supports the creation
of application-specific object interfaces~\cite{weil_rados_2007}. The ability
to offload computation can reduce data movement, and transnational interfaces can
significantly simplify construction of complex storage interfaces that require
uncoordinated parallel access.

An object interface is a plugin structured in a similar way to that of an RPC
in which a developer creates a named function within the cluster that clients
may invoke. In the case of Ceph each function is implicitly run within the
context of an object specified when the function is invoked. Developers of
object interfaces express behavior by creating a composition of native
interfaces or other custom object interfaces, and handle serialization of
function input and output. A wide range of native interfaces are available to
developers, such as reading and writing to a byte stream, controlling snapshots
and clones, all of which may be transactionally composed with access to a
sorted key-value service allowing applications to create rich interfaces, such
as using a read-modify-write guard to protect a shared index defined over
content store in a byte stream.

\begin{figure}[htbp]
\centering
\includegraphics{figures/implementation.png}
\caption{Malacology re-uses Ceph subsystems to manage interface classes.
After the proposal is accepted by the cluster of monitors, the
script is redundantly and consistently distributed to OSDs.
\label{fig:implementation}}
\end{figure}

@@

To this end we have extended the monitoring service using the framework
described in Section~\ref{sec:mon} to provide an interface for registration
and verification of dynamically defined object interfaces. Using this service
guarantees that interface definitions are not only made durable, but are
transparently and consistently propagated throughput the cluster and that
clients are properly synchronized with the latest interfaces.

@@

\paragraph*{Malacology:} New interface hooks are added in strategic spots in
the metadata service to control load balancing and capabilities, and for
defining new file types allowing the indexing service to be re-purposed for
other types of named resources.

@@

{\bf Safely Loading Classes.} The original Mantle API is fragile: the API is
not enforced by the runtime, the system allows strings to be injected through the
admin daemon, constructing the Lua script in C++ is clunky, and the
administrator can inject really bad policies (e.g., while 1) that brings the
whole system down. Malacology exposes the important subsystems of Ceph's
logical storage device framework so that the MDS can safely and dynamically
load policies specified as Lua classes.

@@

The clients retain the best-effort, voluntary release of capabilities, but in
Malacology, the queuing policies are generalized within the MDS to allow for
centralized policies such as fairness or priority.

@@

Ceph provides storage by striping and replicating data across
RADOS~\cite{weil_rados_2007}, the reliable distributed object store. RADOS
uses many techniques to ensure that data is not corrupted or lost, such as
erasure coding, replication, and data scrubbing. Furthermore, many of these
techniques try to be autonomous so that work is distributed across the
cluster. For example, when placement groups change, the OSDs re-balance and
re-shard data in the background in a process called placement group splitting.

@@

\paragraph*{Malacology:} Metadata service policies and object storage interfaces are stored durability
within RADOS and managed by storing references with the object maps. Since
the cluster already propagates a consistent view of these data structures,
we use this service to automatically install interfaces in OSDs, and install
policies within the MDS such that clients and daemons are synchronized on
correct implementations without restarting.

@@

High-performance in CORFU is achieved using a sequencer service that assigns
log positions to clients by reading from a volatile, in-memory counter which
can run at a very high throughput and at low-latency. And since the sequencer
is centralized, ensuring serializability in the common case is trivial.  The
primary challenge in CORFU is handling the failure of the sequencer in a way
that preserves correctness. Failure of the sequencer service in CORFU is
handled by a recovery algorithm that recomputes the new sequencer state using
an application-specific custom storage interface to discover the tail of the
log, while simultaneously invalidating stale client requests using an
epoch-based protocol.

@@

Initially we sought to directly model the sequencer service in Ceph as a
non-exclusive, non-cacheable resource, forcing clients to perform a round-trip
access to the resource at the authoritative metadata server for the sequencer
inode.  Interestingly, we found that the capability system in Ceph uses a
strategy to reduce metadata service load by allowing multiple clients that
open a shared file to temporarily cache the inode resource, resulting in a
round-robin, best-effort batching behavior. When a single client is accessing
the sequencer resource it is able to cache state locally without interruption.

@@

The storage interface is a critical component in the CORFU design. Clients
independently map log positions that they have obtained from a sequencer
service (described in detail in the next section) onto storage devices, while
storage devices provide an intelligent \emph{write}-once, random \emph{read}
interface for accessing log entries. The key to correctness in CORFU lies with
the enforcement of up-to-date epoch tags on client requests; requests tagged
with out-of-date epoch values are rejected, and clients are expected to
request a new tail from the sequencer after refreshing state from an auxiliary
service.  This mechanism forms the basis for sequencer recovery.

In order to repopulate the cached tail value during recovery of a sequencer,
the maximum position in the log must be obtained. To do this, the storage
interface exposes an additional \emph{seal} method that atomically installs a
new epoch value and returns the maximum log position that has been written.
Since the recovery protocol does not inform clients of a new epoch value until
the end of the process, the validity of the tail can be guaranteed despite the
iterative process of contacting storage devices.  Recovery of the sequencer
process itself may be handled in many ways, such as leader election using an
auxiliary service such as PAXOS.

@@

We evaluate the mapping of ZLog onto Malacology by examining the costs of
utilizing the metadata service as a sequencer, and propagating interface
changes throughout the cluster using the monitoring service. We have omitted
evaluation of the overhead costs of adding object interfaces themselves due to
lack of space, and the fact that they are heavily tested and used already in
production with acceptable performance, introducing a small constant overhead
per operation but otherwise does not affect scalability.

@@

\begin{figure}[h]
\centering
\includegraphics{figures/caps-delay-thruput.png}
\caption{Sequencer throughput by reusing various services.
The highest performance is achieved using a single client with
exclusive, cacheable privilege. Round-robin sharing of the sequencer
resource is affected by the amount of time the resource is held,
with best-effort performing the worst.}
\label{fig:captp}
\end{figure}

@@

While a best-effort approach to sharing capabilities makes sense for a file
system client, throughput drops significantly with two clients as the majority
of the time neither client has the capability as it ping-pongs between
clients. This observation reveals a tuning parameter: how long a client
maintains its capability lease. In throughput labeled $2C,<time>$ we show
aggregate throughput as we decrease the amount of time that a client holds its
lease before responding to a request for the capability.  At lease times as
low as 10ms throughput achieve a significant proportion of the locally cached
throughput.

\textbf{The Malacology Approach:} Re-use the capability management features of the MDS.
While the batching mechanism can achieve high-throughput, it is not appropriate
for applications that require predictable latency. The throughput in
Figure~\ref{fig:captp} labeled $2C,ZLog$ corresponds to a centralized
sequencer implementation. While throughput is lower for two clients (because of
the synchronous network round-trip required for each request),
Figure~\ref{fig:capcdf} shows that this approach achieves more predicable
latency compared to all other approaches except for the single client locally
cached mode.

\subsubsection{Interface Propagation}

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-seq-thruput.png}
\caption{A ZLog sequencer that uses the CephFS MDS enjoys the load balancing
capabilities of the metadata cluster. The ``Sequencer Baseline'' has no
background sequencers, while the ``2 Seq'' curves are the throughput
of 1 sequencer when an additional sequencer is running in the background
generating load.}\label{fig:mantle-seq-thruput}
\end{figure}

@@

Figure~\ref{fig:mantle-cpu-utilization} gives a time series graph to show the
behavior of the same workload, 2 sequencers, with balancing turned on and off.
The curves are the throughput (\(y\) axis) over time (\(x\) axis) and the graph
has been partitioned into the two cluster setups. The CPU utilization is
confined to one core the MDS is not multi-threaded, as it has been shown that
metadata performance does not improve with multiple
threads~\cite{konstantinos:pdsw2014-lustre-metadata}.

Overall, the clients achieve lower performance than the capability experiments
in Figure~\ref{fig:captp} because the sequencer uses a slower metadata
operation to manage the capability.  ``Sequencer Baseline" is the best
performance for this particular workload because there is no contention.
Performance is stable and the MDS is under-loaded because we do not see the
spike at the end like the other curves. It appears the bottleneck is somewhere
with the clients -- perhaps it is our 1GBit/s network link. ``2 Seq; No Load
Balancing" shows an overloaded sequencer because the performance of our one
sequencer is low and unstable (high variation in performance). We also deduce
that it is overloaded by comparing to the ``2 Seq; Mantle Load Balancing"
curve, which shows improved performance when load is migrated. At 10 seconds,
the sequencer balancer immediately starts balancing and decides that two
sequencer streams should be split onto two MDSs. It migrates to its neighbor as
per the policy.

@@

We are intending to pursue this work towards the goal of constructing a set
of customization points that allow a wide variety of storage system
services to be configured on-the-fly in existing systems. This work is
one point along that path in which we have looked at targeting
special-purpose storage systems. Ultimately we want to utilize
declarative methods for expressing new services.
